P.berghei pir analysis

### 2021-09-07 chapter3_results_bergheiPir/Manuscript_Github_Pberghei_pir.Rmd
Fix density function and add biplot labels

source('../rfunctions/density_samples_fun.R')
lapply(expt_tpms, 
       density_samples, 
       save = TRUE)
```

@@

pdf(file = 'Manuscript_suppfig1A_corrplot_all_experiments_rnaseq.pdf',
    height = 5,
    width = 5)
corrplot(cor(big_top_recast), method = 'color', 
         order = 'hclust', hclust.method = 'ward.D2',
         cl.lim = c(-0.036,1), tl.cex = 0.50,
         col = c(viridis(100), magma(115)), addrect = 6)
dev.off()

@@

```{r biplot}
pca_object_loadings <- data.frame(Geneid = rownames(big_tpm_pca$x),
                                    big_tpm_pca$x)
pca_object_loadings$Geneid <- paste0(
  pca_object_loadings$Geneid,
  ' ',
  allgene.info$Description[match(pca_object_loadings$Geneid,
                                 allgene.info$Geneid)]
)

plot +
  geom_point(data = pca_object_loadings,
             aes(x = PC1*0.005, y = PC2*0.005),
             inherit.aes = FALSE, size = 0.75)
```

>>>>

source('../rfunctions/density_samples_fun.R')
lapply(expt_tpms, 
       density_samples, 
       save = FALSE)
```

@@

# pdf(file = 'Manuscript_suppfig1A_corrplot_all_experiments_rnaseq.pdf',
#     height = 5,
#     width = 5)
corrplot(cor(big_top_recast), method = 'color', 
         order = 'hclust', hclust.method = 'ward.D2',
         cl.lim = c(-0.036,1), tl.cex = 0.50,
         col = c(viridis(100), magma(115)), addrect = 6)
# dev.off()

@@

```{r biplot}
library('ggrepel')
set.seed(982)

pca_object_loadings <- data.frame(big_tpm_pca$x)

#Remove the large PCA object
rm(big_tpm_pca)

#Calculate the highest loadings, only want these labels

pca_object_loadings$Geneid <- ''

highest_loadings <- pca_object_loadings[rev(
    order(
      apply(
        abs(
          data.frame(pca_object_loadings$PC1, 
                     pca_object_loadings$PC2)),
        1,
        sum)
    )
  )[1:10],]

pca_object_loadings[rev(
  order(
    apply(
      abs(
        data.frame(pca_object_loadings$PC1, 
                   pca_object_loadings$PC2)),
      1,
      sum)
  )
)[1:10],]$Geneid <- 
  allgene.info$Description[match(rownames(highest_loadings),
  allgene.info$Geneid)]

plot +
  geom_point(data = pca_object_loadings,
             aes(x = PC1*0.005, y = PC2*0.005),
             inherit.aes = FALSE, size = 0.75) +
  geom_label_repel(data = pca_object_loadings,
             aes(x = PC1*0.005, y = PC2*0.005,
                 label = Geneid),
             inherit.aes = FALSE, size = 3,
            nudge_x = 0.4,
            force = 100)
```
